Field-informed Reinforcement Learning for Learning Large Scale Collective Tasks

### 2023-05-06 paper.tex
incipit on field coordination approach

>>>>

The field-based coordination approaches utilize a concept of \emph{computational fields} 
 (or simply \emph{fields}), 
 which are \emph{distributed} data structures that associate locations with values and evolve over time. 
A modern field-coordination approach called \emph{aggregate computing}~\cite{Beal2015Computer}
 is rooted in earlier work on \emph{artificial potential fields}~\cite{DBLP:conf/icra/Warren89} and \emph{co-fields}~\cite{DBLP:journals/pervasive/MameiZL04}. 
 In this \emph{macro-programming}~\cite{DBLP:journals/corr/abs-2201-03473} paradigm is possible to devise collective and self-organizing behaviour through a composition of functions operating on fields. 
The fields map a set of individual agents to computational values, 
 allowing them to associate what they sense, process, and actuate. 
Fields are computed locally but subject to a global viewpoint, 
 enabling emergent collective behaviour through the interplay of the system model (similar to the above described) 
 and the \emph{programming model} known as field calculus.
